Simulation-WTCCC

### 2019-11-19 analysis/simulation-WTCCC.Rmd
PVE
simulate phenotype

### Simulate cis-expression 
We simulate cis- expression based on the following model:

@@

### Simulate quantitative phenotype

@@

## Simulation 1: $J$ = No. of all SNPs, $M$ = No. all genes
We simulate quantitative phenotype under several scenarios. First we make all genes with imputed gene expression as causal genes and all SNPs as causal SNPs. This matches our polygenic version of the model.

### 1.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$
We will set $\sigma_e=1$.

### 1.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We will set $\sigma_e=1$.

>>>>

## Simulate cis-expression 
We simulate cis- expression based on the following model:

@@

## Simulate quantitative phenotype

@@

Thus in order to get desired $PVE_{SNP}$ and $PVE_expr$, we set $\sigma_\theta^2$ and $\sigma_\gamma^2$ based on the following formula:

$$\sigma_\theta^2 = \frac{PVE_{SNP}}{M(1-PVE_{SNP} - PVE_{expr})}$$
$$\sigma_\gamma^2 = \frac{PVE_{expr}}{Jvar(\tilde{X})(1-PVE_{SNP} - PVE_{expr})}$$

## Simulation 1: $M$ = No. of all SNPs, $J$ = No. all genes
We simulate quantitative phenotype under several scenarios. First we make all genes with imputed gene expression as causal genes and all SNPs as causal SNPs. This matches our polygenic version of the model.

### 1.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$
We set $\sigma_e=1$.

### 1.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

## Simulation 2: $M$ = No. of all SNPs, $J$ = ~10% all genes (J=2000)

### 2.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$
We set $\sigma_e=1$.

### 2.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

## Simulation 3: $M$ = ~ 10% all SNPs (M=50000), $J$ = No. all genes

### 3.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$ 
We set $\sigma_e=1$.

### 3.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.

## Simulation 4: $M$ = ~ 10% all SNPs (M=50000), $J$ = ~10% all genes (J=2000)

### 4.1 $PVE_{SNP}=0.1$, $PVE_{expr}=0.1$ 
We set $\sigma_e=1$.

### 4.2 $PVE_{SNP}=0.1$, $PVE_{expr}=0.4$
We set $\sigma_e=1$.
